Predict Models

### 2024-01-03 scripts/predict_models.Rmd
subset layers before crop

@@

  # read in occurrences and subset prediction to 100 miles from border
  bound <- sf::st_read(occ_path, quiet = TRUE) |>
    dplyr::filter(Occurrence == 1) |>
    sf::st_union() |>
    sf::st_convex_hull() |>
    sf::st_buffer(160934) |>
    sf::st_bbox()

  pout <- '../results/suitability_maps'
  layer_subset <- terra::crop(layers, bound)
  terra::predict(
    type = 'prob', cores = 8,
    layer_subset, sdm, cpkgs="randomForest",
    filename = file.path(pout, paste0(x$species, '.tif')),
    wopt = c(names = 'predicted_suitability'))

@@

lapply(models_occ[3], predict_wrapper)

r <- terra::rast('../results/suitability_maps/Acamptopappus_sphaerocephalus.tif')
plot(r)

```

```{r}

g <- readRDS('../results/rf_models/Abronia_villosa-2023-12-30_14:48:33.rds')

```

>>>>

setGDALconfig(c("GDAL_MAX_DATASET_POOL_SIZE=1024"))

@@

  # read in occurrences and subset prediction to 100 miles from border
  bound <- sf::st_read(occ_path, quiet = TRUE) |>
    dplyr::filter(Occurrence == 1) |>
    sf::st_union() |>
    sf::st_convex_hull() |>
    sf::st_buffer(80467) |>
    sf::st_bbox()

  pout <- '../results/suitability_maps'
  layers <- terra::subset(layers, term_grab(sdm))
  layer_subset <- terra::crop(rast(layers, bound)
  terra::predict(
    type = 'prob', cores = 16,
    layer_subset, sdm, cpkgs="randomForest",
    filename = file.path(pout, paste0(x$species, '.tif')),
    wopt = c(names = 'predicted_suitability'))

@@

setGDALconfig(c("GDAL_MAX_DATASET_POOL_SIZE"),  c(""))

lapply(models_occ[c(5)], predict_wrapper)
```

```{r}
achy <- rast('../results/suitability_maps/Achnatherum_hymenoides.tif')
plot(achy[[2]])
```
